\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}
After three exiting years my work on this thesis is done. It would not have been possible without the help of many people, to all of whom I am very grateful. 

First of all, I would like to thank Prof. Dr. Lutz Feld for giving me the opportunity to work on this interesting topic and for supervising my thesis. In the last three years, I have always profited from his constant support and advise.

I would like to thank Prof. Dr. Michael Kr\"amer for agreeing to be the second referee of this work. 

My current and former colleagues in the analysis group, Dr. Christian Autermann, Matthias Edelhoff, Knut Kiesel, Christian Schomakers, Daniel Sprenger, and Johannes Schulz, all contributed to a very productive but also pleasant workplace and I would like to thank them for that. Many thanks for the great atmosphere in the working group belong also to Prof. Dr. Lutz Feld, Dr. Katja Klein, Martin Lipinski, Marius Preuten, Max Rauch, Sarah B\"ohm and Jan Sammet.  

I joined the dilepton edge search at an exiting time. Daniel Sprenger and Matthias Edelhoff were immensely helpful in this fist months, introducing me to the analysis and making me feel at home among my new colleagues very quickly. Thank you!  

I would like to thank Christian Schomakers for the fruitful cooperation in the last years and his valuable contributions to the interpretation of the analysis results.  

Many people within the CMS collaboration have contributed to the success of this analysis. I would like to thank all the people involved in the review of this analysis, especially the SUSY group conveners David Stuart, Eva Halkiadakis, Frank W\"urthwein, Keith Ulmer, and Filip Moortgart, and the conveners of the leptonic subgroup, Didar Dobur, Benjamin Hooberman, Petar Maksimovich, and Wolfgang Adam. Valuable feedback during the review process was also provided by the analysis review committee. For the fruitful collaboration during the analysis I would especially like to thank Marco-Andrea Buchmann, Pablo Martinez, Frederic Ronga and Konstantinos Theofilatos. Thanks also to Benjamin Hooberman, Dominick Olivito, and Vince Welke for their contributions to the on-Z part of the analysis. 

Many thanks go also to the LHC team and the CMS collaboration for constructing and operating the magnificent accelerator and detector which together provided me with the dataset necessary for my work.    

No data analysis is possible without computing infrastructure. Therefore, I am very grateful to Thomas Kress, Andreas Nowack, Oleg Tsigenov, and Michael Bontenackels for maintaining both the Aachen T2 grid cluster and the desktop PC cluster.   

Many thanks to all my friends who have accompanied me on my way and provided a much needed balance to my work all this time. Some of them I have known all my life, some I have met along the way, but all are a valuable part of my life. I especially want to thank Sebastian, Klaas, Knut and two Christians for reading this thesis and providing valuable criticism. 

Most of all, I would like to thank my family. My parents have been a great support throughout all my studies, both emotionally and financially, and I am forever grateful to them. I always enjoy being home with them and my sisters and brother. Also, I want to thank my grandmother and my late grandfather for always believing in my goals and for their great support throughout the years.  