\section{Trigger and event processing}
\section{Object reconstruction}
The physics objects relevant to this analysis are electrons, muons, jets and the missing transverse energy \MET. Here the reconstruction of these objects from the information provided by the CMS detector is described. While the electron and muon candidates used here are reconstructed independent of each other with dedicated algorithms, jets and \MET are provided by the particle flow (PF) algorithm. It combines information from all subdetectors to achieve a consistent description of the full event. 
\subsection{Muon reconstruction and selection}
The track of a muon is reconstructed separately in the inner tracker and the muon system, resulting in a $\textit{tracker track}$ and a $\textit{standalone muon}$. 

Tracks in the inner tracker are reconstructed using a method called Combinatorial Track Finder (CTF)~\cite{Chatrchyan:2014fea}, which performs pattern recognition and track fitting employing a Kalman filter technique~\cite{Fruhwirth1987444}. The track is described by a five-dimensional state vector, whose initial parameters are taken from track seeds, determined from three hits or two hits and a vertex constraint in the pixel detector or the innermost layers of the strip detector. The state vector is extrapolated to the next tracker layer taking into account uncertainties and energy losses due to interactions with the tracker. If tracker hits are found in the modules where they are expected from the extrapolation, they are added to the track candidate. If no hits are found, a ghost hit is added to the track to account for inefficiencies in the hit reconstruction. A track fit is then performed to all hits associated with the track candidate, using again Kalman filtering and smoothing. This procedure is performed iteratively, each time removing the hits already associated to a track candidate and relaxing the requirements on the track seeds to allow for reconstruction of track with low \pt or not originating from the primary interaction. In the reconstruction of the data taken in 2012, seven iterations were performed~\cite{SWGuideIterativeTracking}. 

For the reconstruction of $\textit{standalone muons}$ in the muon system, the hits inside the individual muon chambers are fitted to generate track segments, providing first estimates of the track parameters under the hypothesis that the muon was created in the interaction region and was travelling through the muon system from the inside out. These segments are used as starting points for a track reconstruction using all hits from the DTs, CSCs and RPCs, again using the Kalman filtering technique~\cite{1748-0221-5-03-T03022}.

Tracker tracks are promoted to $\textit{tracker muons}$ when they can be matched to a track segment in the muon detector. $\textit{Standalone muons}$ are matched to tracks from the inner tracker. If a compatible track is found a combined fit to all hits of the track and the $\textit{standalone muon}$ is performed, resulting in a $\textit{global muon}$. The PF algorithm applies further selection requirements to the reconstructed $\textit{global}$ and $\textit{track muons}$, introducing a fourth category, the $\textit{particle flow muon}$~\cite{CMS-PAS-PFT-10-003}. 

Muons selected in this analysis are required to be reconstructed as $\textit{tracker}$, $\textit{global}$ and $\textit{particle flow}$ muons. The $\chi^2$ per degrees of freedom of the track fit must not exceed 10. Several requirements on the information available for the different track fits are made: At least one muon chamber hit must be included in the track fit of the $\textit{global muon}$. For the fit of the $\textit{tracker muon}$ at least one hit in the pixel detector and six layers with hits in the strip detector have to be available. Also the track from the inner tracker has to be matched to at least two track segments in the muon chambers. To ensure that the muon originates from the primary interaction and to suppress backgrounds from cosmic muons the impact parameter of the track with respect to the primary vertex must not exceed $\unit{0.02}{\centi\meter}$ in the $x$-$y$ plane and $\unit{0.1}{\centi\meter}$ in $z$ direction. Selected are muons with a \pt larger than $\unit{10}{\giga\electronvolt}$ and $|\eta|$ less than 2.4. The muon selection is summarized in Table~\ref{tab:muonID}.
\begin{table}
\begin{center}
\begin{tabular}{c|c}
Criterion & Selection \\
\hline \hline 
\multicolumn{2}{c}{Acceptance} \\
\hline
\pt & $> \unit{10}{\giga\electronvolt}$ \\
$|\eta|$ & $< 2.4$ \\
\hline
\multicolumn{2}{c}{Muon ID} \\
\hline
Required to be a & $\textit{tracker muon}$ \\
 & $\textit{global muon}$ \\
 & $\textit{particle flow muon}$ \\
 \hline
 \multicolumn{2}{c}{Track quality} \\
 \hline
  $\chi^2/N_{dof}$ & $< 10 $ \\
  valid muon hits & $> 0 $ \\
  matched stations & $> 1 $ \\
  valid pixel hits & $ > 0 $ \\
  tracker layers with hits & $ > 6 $ \\
\hline
  \multicolumn{2}{c}{Impact parameter} \\
\hline
	$d0 = \sqrt{dx^2 + dy^2}$ & $< \unit{0.02}{\centi\meter}$ \\
	dz & $ < \unit{0.1}{\centi\meter}$ \\  
\end{tabular}
\caption{Summary of requirements of the muon selection.}
\label{tab:muonID}
\end{center}

\end{table}
\subsection{Electron reconstruction and selection}
The signature of an electron in the CMS detector is a track reconstructed by the tracking detectors that leads to a matching cluster of energy reconstructed in the ECAL. In practice this is complicated by the large material budget of the tracking detectors, resulting in a high probability of an electron to loose energy in form of bremsstrahlung. About 35\% of all electrons loose more than 70\% of their energy and for 10\% the energy loss exceeds 95\%~\cite{Baffioni:2006cd}. The reconstruction is further complicated by the large solenoidal magnetic field, which bends the electron's trajectory away from the radiated photons, leading to a spread of the energy in $\phi$ direction. This has to be taken into account both in the tracking algorithms and the clustering of the energy deposits in the ECAL. 

In the ECAL two different algorithms are used to group the energy deposits into clusters and clusters of clusters, called super clusters (SCs), in the barrel and endcap regions of the detector. Both are designed to group together the energy deposits of the electron itself and those of the bremsstrahlung photons. In the of $1.6 < |\eta| < 2.6$ the preshower is located in front of the ECAL and electrons will deposit a fraction of their energy there. The energy deposited in the strips of the preshower between an SC in the ECAL and the primary vertex is summed and added to the energy of this SC~\cite{Anderson:1365024}. ADD SC position calculation! 

In the track reconstruction with Kalman filters as discussed above energy losses due to interactions of the particles with the tracker material are considered to be Gaussian. For electrons, however, this is not sufficient because the dominant energy loss due to bremsstrahlung is a non-gaussian contribution. Electron candidate tracks are therefore fitted with a Gaussian Sum Filtern (GSF) algorithm~\cite{FruhwirtGSFCMS}, which models the non-Gaussian components as a sum of Gaussian distributions. GSF tracking is initiated in two ways. $\textit{ECAL driven seeding}$ requires the presence of a track seed that matches the position of an SC when extrapolating backwards from the ECAL to track~\cite{Baffioni:2006cd}. Alternatively, $\textit{tracker driven seeding}$ is started by tracks that either match the position of ECAL clusters when extrapolated to the ECAL surface, covering the case of no bremsstrahlung, or are of poor quality with only few associated hits~\cite{Chatrchyan:2014fea}. The GSF track and the energy measurement in the ECAL are combined into the final electron candidate. 

Electrons are selected requiring \pt larger than $\unit{10}{\giga\electronvolt}$ and $|\eta| < 2.5$. The gap region between ECAL barrel and endcaps of $1.442 < |\eta| < 1.566$ is exluded. To suppress background from muons that radiate photons electrons with a distance of $\Delta R = \sqrt{\Delta\phi^2 + \Delta \eta^2}$ to the nearest $\textit{global}$ or $\textit{tracker muon}$ less than 0.1 are rejected. Backgrounds from photon conversion, decays of heavy flavour quarks  or charged hadrons are suppressed by a set of selection criteria. The matching of track and supercluster is quantified by the differences between the supercluster position and the parameters of the track extraploated from the vertex to the ECAL surface in $\Delta\phi$ and $\Delta\eta$. As the energy of the electron is contained in the ECAL, the ratio of hadronic energy deposited in the HCAL behind the electron candidate must be small. The energy spread in the ECAL due to bremsstrahlung occurs in $\phi$ direction. Therefore no significant spread of the energy in $\eta$, parametrized as
\begin{equation}
\sigma_{i\eta i\eta} = \frac{\sum\limits_i^{5\times 5} w_i\cdot (\eta_i - \bar{\eta}_{5\times 5})^2}{\sum\limits_{i}^{5\times 5} w_i},
\end{equation}
\begin{equation}
w_i = max(0,4.7 + ln(\frac{E_i}{E_{5 \times 5}})),
\end{equation}
is expected, where for $5\times 5$ crystals around the seed crystal the distance in $\eta$ from the mean $\eta$ of the cluster is summed, weighted by the energy deposit in each crystal. For a well measured electron there is good agreement between the energy deposited in the ECAL and the track momentum measured at the vertex. Therefore the value of $| \frac{1}{E} - \frac{1}{p}|$ must be small. Requirements on the impact parameter of the track with the respect to the vertex are made. Two requirements are applied to reject electrons from converted photons. Only one pixel layer with missing hit is allowed, rejecting most conversions occurring after the first layer of the pixel detectors. To reject also conversion in this first layer and in the beam pipe, vertex fits for the electron track with neighbouring tracks are performed in order to reconstruct the point of conversion. For a prompt electron, the probability of these fits is low. Some of these requirements are already applied on HLT level. In order to select electrons for which the trigger is fully efficient, selections at least as strict are applied at analysis level. The specific requirements are listed in Table~\ref{tab:eleID}, separately for barrel and endcap when appropriate. 
\begin{table}
\begin{center}
\begin{tabular}{c|c|c|c|c}
Criterion & \multicolumn{2}{c|}{Selection at HLT}  & \multicolumn{2}{c}{Selection at Analysis Level}  \\
 & EB & EE & EB & EE \\
\hline \hline 
\multicolumn{5}{c}{Acceptance} \\
\hline
\pt & \multicolumn{2}{c|}{trigger dependent} &  \multicolumn{2}{c}{$> \unit{10}{\giga\electronvolt}$} \\
$|\eta|$ & \multicolumn{2}{c|}{$< 2.5 $} & \multicolumn{2}{c}{$< 2.5 $, excluding $1.442 < |\eta| < 1.566$}  \\

\hline
\multicolumn{5}{c}{ID variables} \\
\hline
$|\Delta \eta |$ & 0.01 & 0.01 & 0.007 & 0.009  \\
$|\Delta \phi |$ & 0.15 & 0.10 & 0.15 & 0.10  \\
$\sigma_{i\eta i\eta}$ & 0.011 & 0.031 & 0.01 & 0.03  \\
$H/E$ & 0.10 & 0.075 & 0.12 & 0.10 \\ 
$|\frac{1}{E} - \frac{1}{p}|$ & \multicolumn{2}{c|}{-} & 0.05 & 0.05 \\
\hline
\multicolumn{5}{c}{Conversion rejection} \\
\hline
 missing pixel hits & \multicolumn{2}{c|}{-} & $\leq1$  & $\leq1$ \\
 vertex fit probability & \multicolumn{2}{c|}{-} & $< 10^{-6}$ & $< 10^{-6}$ \\ 
 \hline
  \multicolumn{5}{c}{Impact parameter} \\
\hline
	$d0 = \sqrt{dx^2 + dy^2}$ & \multicolumn{2}{c|}{-} & $< \unit{0.02}{\centi\meter}$ & $< \unit{0.02}{\centi\meter}$\\
	dz & \multicolumn{2}{c|}{-} & $ < \unit{0.1}{\centi\meter}$ & $ < \unit{0.1}{\centi\meter}$\\  
\end{tabular}
\caption{Summary of requirements of the electron selection.}
\label{tab:eleID}
\end{center}
	
\end{table}
\subsection{Observables reconstructed with Particle Flow}
\subsubsection{The algorithm}
The particle flow (PF) algorithm is designed to combine information from all subdetectors to reconstruct a consistent description of the event, resulting in a list of reconstructed particles. The basic building blocks are PF elements, which are reconstructed in each subdetector separately: Tracks of charged particles in the tracker, energy clusters in the calorimeters and muon tracks in the muon system. A linking algorithm then combines elements into blocks based on their geometrical distance, for example by extrapolating a track into the ECAL and HCAL and searching for compatible clusters. Similarly, calorimeter clusters are linked between the preshower, ECAL, and HCAL and tracks from the tracker are associated with those from the muon system. The reconstruction of $\textit{particle candidates}$ is performed on the elements inside a block. Muons are reconstructed first, followed by electrons, for which, similar to the standard algorithm described above, a refit of the track with the GSF algorithm is performed and bremsstrahlung photons are collected in the ECAL. Lastly, calorimeter clusters compatible with a track are identified as charged hadron, while clusters without a matching track are either categorized as neutral hadrons, or, if no or only small energy deposits in the HCAL exist, as photons~\cite{CMS-PAS-PFT-09-001}. 
\subsubsection{Jets}
The jets of particles produced in the hadronization of quarks and gluons are grouped together by clustering algorithms. An anti-$k_T$ algorithm~\cite{Cacciari:2008gp}, performed using a fast implementation~\cite{Cacciari:2011ma,Cacciari:2005hq}, is used in this analysis.  Input to the clustering are the $\textit{particle candidates}$ reconstructed by the particle flow algorithm.

The anti-$k_T$ algorithm is a sequential clustering algorithm. Two distance measures are introduced, the first between two particles or pseudo-jets $i$ and $j$ and the second between particle or pseudo-jet $i$ and the beam axis: 
\begin{equation}
d_{ij} = min(k_{Ti}^{-2},k_{Tj}^{-2})\frac{\Delta^2_{ij}}{R^2},
\end{equation}
\begin{equation}
d_{iB} = k_{ti}^{-2},
\end{equation}
with $\Delta_{ij}^2 = (y_i-y_j)^2 + (\phi_i - \phi_j)^2$ and $k_{Ti}$, $y_i$, and $\phi_i$ being the transverse momentum, rapidity and azimuth of a particle. For an entity (particle, pseudo-jet) $i$ all distances are calculated. If the smallest is a $d_{ij}$, $i$ and $j$ are combined in a new pseudo-jet. If the smallest distance if the distance to the beam $d_{iB}$, the pseudo-jet is considered a final jet and removed from the list of particles available for clustering. 

The measured jet energy has to be corrected for energy offsets and the non-uniform and non-linear response of the detector. Each component of the jet's four-momentum vector is corrected by a multiplicative factor~\cite{1748-0221-6-11-P11002}
\begin{equation}
p_{\mu}^{cor} = C \cdot p_{\mu}^{raw}.
\end{equation} 
The correction is applied as a sequence of different factors: 
\begin{equation}
C = C^{L1}_{\text{offset}}(p_T^{raw})\cdot C^{L2L3}_{MC}(p_T^{\prime},\eta)\cdot C^{L2Residual}_{rel}(\eta) \cdot C^{L3Residual}_{abs}(p_T^{\prime\prime}).
\end{equation}
The L1 correction, applied to the raw jet, corrects for offsets due to the underlying event and pileup. The L2L3 corrections, derived from Simulation, corrects for the non-linearities and non-uniformities of the detector response to jets of different $\pt$ and $\eta$ and is applied to the offset-corrected jet. To correct for the differences between Simulation and real data, jets in data events are further corrected for the residual differences between the two.  

In this analysis, the \pt of a jet is required to exceed $\unit{40}{\giga\electronvolt}$ and jets are required to lie inside the fiducial volume of the ECAL of $|\eta| < 3.0$. A set of loose quality selections is applied to suppress jets reconstructed because of detector noise, ensuring that the jet is reconstructed in more than one subdetector and has more than one constituent. As the jet clustering is performed using all reconstructed $\textit{particle candidates}$, jets within $\Delta R = 0.4$ to leptons identified with the criteria described above are rejected. 
\section{Datasets}
\section{Event selection}